---
title: "Regression of Binary Outcome Data"
date: "Created: 2017-11-22 <br> Updated: `r Sys.Date()`"
output: html_notebook
---

When you want to make a change to the template, do so by going to:

Applications > Contents > Resources > resources > templates > r_markdown_notebook_osx.Rmd

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r load_packages, message=FALSE}
library(tidyverse)
```

Need to do a comprehensive tutorial on regression methods for binary outcome including:

* What is the relationship between ORs and RRs?

* Calculate Mantel Hanzel statistics

* How to use glm in R

* How to intepret glm output - including the log odds

* Calculating RR's using Poisson with sandwich estimator

    + https://academic-oup-com.proxy.hsc.unt.edu/aje/article/159/7/702/71883
    
* Intepret the output of this method

* Compare all methods to SAS

* What is the best way to work with multiple models? Model building?

    + See the stuff I've already done in STEP analysis_evaluation_explore

* Assumptions at each step above?

-------------------------------------------------------------------------------

# Load data




-------------------------------------------------------------------------------

&nbsp;

#### Session Info:
```{r session_info, echo=FALSE}
sessionInfo()
```
