---
title: "Set time zone in R markdown"
author: "Brad Cannell"
date: "Created: 2017-12-24 <br> Updated: `r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{timezone}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
Sys.setenv(TZ = "US/Central")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Adding a timezone to an Rmd files

For awhile I was getting a weird warning message:

`Warning message:
In as.POSIXlt.POSIXct(x, tz) : unknown timezone 'default/America/Chicago'`

To fix I used info from a mix of the following websites:

https://www.r-bloggers.com/doing-away-with-%E2%80%9Cunknown-timezone%E2%80%9D-warnings/

https://stackoverflow.com/questions/4047188/unknown-timezone-name-in-r-strptime-as-posixct

https://stackoverflow.com/questions/24880493/how-to-find-out-r-library-location-in-mac-osx

This code told me what my current system timezone was set to:

```{r}
Sys.timezone() # Originally returned NA
```

This code told me where R was installed on my machine:

```{r}
.Library
```

Then I looked for the the file "/Library/Frameworks/R.framework/Versions/3.4/Resources/share/zoneinfo" for the most appropriate time zone to use.

I reset the timezone using this code:

```{r}
Sys.setenv(TZ = "US/Central")
```

Then I checked again:

```{r}
Sys.timezone()
```

Seems to be working for now.
